### 2020-03-21 README.Rmd
run_cv changes and README changes
sill pugging away at `run_cv`

```{r}
library(tidyverse)
library(forestecology)
library(snakecase)
library(skimr)
library(sf)
library(sfheaders)
# devtools::install_github("rvalavi/blockCV")
library(blockCV)
```

@@

```{r}
scbi_cv_predict <- focal_vs_comp_scbi %>%
  run_cv(model_specs = scbi_specs, max_dist = max_dist, cv_grid = scbi_cv_grid)

>>>>

```{r}
library(tidyverse)
library(forestecology)
library(snakecase)
library(skimr)
library(sf)
library(sfheaders)
# devtools::install_github("rvalavi/blockCV")
library(blockCV)
library(tictoc)
```

@@

Here I cheated `run_cv` to run the cross valididation for just two training set. It runs on the whole data set up just for `test = fold 23` and `test = fold 2`. Just to see how long it takes.
```{r}
tic()

scbi_cv_predict <- focal_vs_comp_scbi %>%
  run_cv(model_specs = scbi_specs, max_dist = max_dist, cv_grid = scbi_cv_grid)
toc()
```

Running just two folds took 5440 seconds. There are 28 folds. So running everything should take 5440 * 14 / 60 / 60 = 21 hours.

Comapre results

```{r}

scbi_cv_predict %>%
  inner_join(scbi_growth_df, by = 'focal_ID', suffix = c('_cv','')) %>%
  summarise(rmse_cv = sqrt(mean((growth - growth_hat_cv)^2)),
            rmse = sqrt(mean((growth - growth_hat)^2)) )
